Verifying the \shaThree\ Implementation from \openssl\ with the Software Analysis Workbench

### 2022-05-13 paper/paper.tex
Style and caption fig 5

\documentclass[runningheads]{llncs}
%
\usepackage{paralist}
\usepackage{comment}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\definecolor{blue}{RGB}{42,0,255}
\definecolor{green}{RGB}{63,127,95}
\definecolor{purple}{RGB}{127,0,85}
\definecolor{lime}{RGB}{114, 148, 0}
\usepackage{listings}
\lstdefinelanguage{Cryptol}{
  keywordstyle=[1]\color{blue}\bfseries,
  keywordstyle=[2]\color{purple}\bfseries,
  keywordstyle=[3]\color{black}\bfseries,
  basicstyle={\color{lime}\scriptsize},
  literate=*
  {*}{{{\color{black}$*$}}}{1}
  {=}{{{\color{black}=}}}{1}
  {+}{{{\color{black}+}}}{1}
  {-}{{{\color{black}$-$}}}{1}
  {\%}{{{\color{black}\%}}}{1}
  {(}{{{\color{black}(}}}{1}
  {)}{{{\color{black})}}}{1}
  {\{}{{{\color{black}\{}}}{1}
  {\}}{{{\color{black}\}}}}{1}
  {[}{{{\color{black}[}}}{1}
  {]}{{{\color{black}]}}}{1}
  {|}{{{\color{black}$|$}}}{1}
  {>}{{{\color{black}$>$}}}{1}
  {<}{{{\color{black}$<$}}}{1}
  {\#}{{{\color{black}\#}}}{1}
  {@}{{{\color{black}@}}}{1}
  {.}{{{\color{black}.}}}{1}
  {\'}{{{\color{black}'}}}{1}
  {:}{{{\color{black}:}}}{1}
  {^}{{{\color{black}$\char`\^$}}}{1}
  {&}{{{\color{black}\textbackslash}}}{1},
  morekeywords=[1]{Bit, Integer, STATE_ARR, W, COL, type, LIST4, LIST63, True, False},
  morekeywords=[2]{if, then, else, where},
  morekeywords=[3]{pi, rc, cond, a, b, x, y, z, for, n, r, R, f, rs, i, index, t, 
    vals, loop, state, while, take}
}

>>>>

\documentclass[runningheads]{llncs}
%
\usepackage{paralist}
\usepackage{comment}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\definecolor{blue}{RGB}{42,0,255}
\definecolor{green}{RGB}{63,127,95}
\definecolor{purple}{RGB}{127,0,85}
\definecolor{lime}{RGB}{114, 148, 0}
\usepackage{listings}
\lstdefinelanguage{Cryptol}{
  keywordstyle=[1]\color{blue}\bfseries,
  keywordstyle=[2]\color{purple}\bfseries,
  keywordstyle=[3]\color{black}\bfseries,
  basicstyle={\color{lime}\scriptsize},
  literate=*
  {*}{{{\color{black}$*$}}}{1}
  {=}{{{\color{black}=}}}{1}
  {+}{{{\color{black}+}}}{1}
  {-}{{{\color{black}$-$}}}{1}
  {\%}{{{\color{black}\%}}}{1}
  {(}{{{\color{black}(}}}{1}
  {)}{{{\color{black})}}}{1}
  {\{}{{{\color{black}\{}}}{1}
  {\}}{{{\color{black}\}}}}{1}
  {[}{{{\color{black}[}}}{1}
  {]}{{{\color{black}]}}}{1}
  {|}{{{\color{black}$|$}}}{1}
  {>}{{{\color{black}$>$}}}{1}
  {<}{{{\color{black}$<$}}}{1}
  {\#}{{{\color{black}\#}}}{1}
  {@}{{{\color{black}@}}}{1}
  {.}{{{\color{black}.}}}{1}
  {\'}{{{\color{black}'}}}{1}
  {:}{{{\color{black}:}}}{1}
  {^}{{{\color{black}$\char`\^$}}}{1}
  {&}{{{\color{black}\textbackslash}}}{1},
  morekeywords=[1]{Bit, Integer, STATE_ARR, W, COL, type, LIST4, LIST63, True, False},
  morekeywords=[2]{if, then, else, where},
  morekeywords=[3]{pi, rc, cond, a, b, x, y, z, for, n, r, R, f, rs, i, index, t, 
    vals, loop, state, while, take, nextR}
}
